### 2015-02-11 paper_20_sdo.tex
cleaning up references, removing journal abbreviations and spelling out full months
added another Capers Jones book
availability updates

    Software engineering has struggled to determine the correct projects to complete \cite{DeMarco2009}.
    Software projects are typically behind schedule and over budget. Organizations need a better
    technique to understand the past performance so they can better predict the future performance.

>>>>

    Software engineering has struggled to determine the correct projects 
    to complete \cite{DeMarco2009}.
    Software projects are commonly behind schedule and over budget \cite{Lehtinen2014, 
    Charette2005,Jorgensen2013,Ichu2012} with nearly 20\% of projects
    in the United States still failing \cite{Emam2008}. 
    As of 2015, Software engineering is 
    still awaiting the professional status of more established fields such
    as medicine, law, and general engineering \cite{Jones2013b}. 
    Organizations need a better
    technique to understand the past performance so they can better 
    predict the future performance.  Proper measurement will be essential
    to solidifying software engineering as certified profession.

### 2015-02-11 paper_40_mpi.tex
availability updates

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.  
            The following algorithm will calculate the score of software availability.
            \begin{displaymath}
               S_{3_i} = \left\{
                 \begin{array}{lr}
                   \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
                   \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
                 \end{array}
               \right.
            \end{displaymath} 
            \[
                S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
            \]

@@

            Application ID & String  & Required \\
            \myrowcolour%
            Frequency Date & Date & Required \\
            Uptime & Float & Optional \\
            \myrowcolour%
            Scheduled Downtime & Float & Optional \\
            Unscheduled Downtime & Float  & Optional \\
            \myrowcolour%
            Percent Uptime & Float & Required \\
            Expected Percent Uptime & Float & Required \\

            \caption{AVAILABILITY DATA NEEDED FOR MPI}
            \label{tab:avail}
            \end{longtable}

>>>>

        \subsubsection{AVAILABILITY}
            All the new requirements and great quality do not matter if the software is not available.
            All the new features and great quality do not matter if the software is not available.  Thus it
            is essential to set an expected Service Level Agreement (SLA)\footnote{For an SDO, an SLA is a 
            contract specifying the amount of time software will be available during a
            given time period. } and measure 
            performance against that SLA.  The following section will outline to data needed to properly
            calculate an SLA and the data needed to calculate the MPI score for availability.

            Special Note: The System ID for availability does not have to be the same
            as the Application ID for quality or any of the other elements.  Some 
            organizations have a one-to-one mapping between Applications being developed
            and systems being deployed.  Others have more complex sceranios that require
            multiple applications to be combined to form a system.  Then the availability
            of the system is tracked.

            \paragraph{AVAILABILITY DATA}
                Table \ref{tab:availdata} identifies the necessary data to calculate
                the MPI element score for availability.  Notice the three optional 
                fields: \textit{Uptime}, \textit{Scheduled Downtime}, and 
                \textit{Unscheduled Downtime}; they are optional because they can be
                used to calculated the \textit{Percent Uptime}.  The \textit{Percent Uptime}
                is the important value for the MPI schedule score.  Here are the two common
                approaches for calculating percent uptime:

                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
                \]
                and the alternative method
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
                \]
                The only difference is the removal of scheduled downtime from 
                the calculation.  The calculation approach is typically specified in
                the contract associated with the SLA.

                    System ID & String  & Required \\
                    \myrowcolour%
                    Frequency Date & Date & Required \\
                    Uptime & Float & Optional \\
                    \myrowcolour%
                    Scheduled Downtime & Float & Optional \\
                    Unscheduled Downtime & Float  & Optional \\
                    \myrowcolour%
                    Percent Uptime & Float & Required \\
                    Expected Percent Uptime & Float & Required \\

                    \caption{AVAILABILITY DATA NEEDED FOR MPI}
                    \label{tab:availdata}
                \end{longtable}

            \paragraph{AVAILABILITY FORMULA}
            \begin{displaymath}
               S_{3_i} = \left\{
                 \begin{array}{lr}
                   \text{where } A_{a_i} \leq A_{e_i} & : \left[ \frac{A_{a_i} - A_{e_i}}{A_{e_i}} \right] \\
                   \text{where } A_{a_i} > A_{e_i}  & : \left[ \frac{A_{a_i} - A_{e_i} }{1-A_{e_i}} \right]
                 \end{array}
               \right.
            \end{displaymath} 
            \[
                S_3 = \frac{\sum^n_{i=1}S_{3_i}}{n}
            \]

@@
